Article Title

### 2013-12-18 plos.tex
edited discussion

\section*{Discussion}
\subsection*{Neural correlations as indicators of functional connectivity}
Neural correlations have a rich history in neuroscience as indicators of \emph{functional connectivity}. When measured on temporal scales of a few milliseconds, peaks in the cross-correlations between pairs of neurons at latencies typical of synaptic transmission are often interpreted as evidence of direct synaptic connections between pairs of cells \cite{Moore:1970,Alonso:1998,Denman:2013}. Without targeted stimulations of specific cells or measurements of intracellular signals, such analysis remains the best test for probable monosynaptic connections in vivo. At longer temporal scales, neural correlations reflect activations involving large ensembles of neurons. Such correlations may have emergent structure with little  correspondence to synaptic connectivity, which  may better reflect computations performed by the circuit.  For this reason, firing rate correlations at scales of tens or hundreds milliseconds have been of interest for their implications on coding under the assumption of rate codes and linear downstream decoder \cite{Averbeck:2006}. The terms \emph{functional connectivity} is still often applied to slow correlations, similarly to its use in PET, fMRI, EEG, and MEG brain imaging studies, as an expression of task-related, stimulus-evoked, or spontaneous synchronization or correlation between brain regions, circuits, or cells without implying a mechanistic interpretation.

@@

\subsection*{Correlation `structure'}
The term `structure' implies a reduced, simplified representation expressing the essential organization.  The structure of slow correlations is often expressed through low-rank approximations extracted by principal component analysis or factor analysis. These components show synchronous multineuronal activation patterns without revealing graphs of interactions between neurons.

Another reduced representation of correlation matrices is obtained by sparsifying its inverse, resulting in a graph of partial correlations. Under the assumption of a multivariate normal distribution or, more generally, an elliptical distribution, sparse partial correlations suggest a sparse matrix of dependencies, a probabilistic graphical model. This property has led some investigators to suggest that, in brain imaging studies, such approximation must serve as better proxies of direct interactions between brain regions than correlations \cite{Varoquaux:2012,Ryali:2012}.

\subsection*{Interpretation of functional connectivity from population calcium signals}
Nonetheless, some investigators have examined graphs of the most significant correlations in population calcium activity as proxy of connectivity \cite{Malmersjo:2013}.

While synaptic connectivity constitutes a directed weighted graph, most meaningful representation of functional organization at longer temporal scales are less certain. A common approach has been to examine the low-rank structure of the joint population activity extracted through principal component analysis, factor analysis, independent component analysis, linear embedding, and others. Functional connectivity is then represented as the eigenvectors, principle components, or factor loadings corresponding to the extracted components of the joint activity.

If only most significant components are retained, these two representations turn into, respectively, low-rank approximations and sparse inverse approximations. Low-rank representation suggest interpretation as common input onto large subsets of neurons or highly synchronous activations in the entire recorded population.

>>>>

\section*{Discussion}
\subsection*{Neural correlations as indicators of functional connectivity}
Neural correlations boast a rich history in systems neuroscience as indicators of \emph{functional connectivity}. When measured on temporal scales of a milliseconds, peaks in the cross-correlogram between pairs of neurons at latencies typical of synaptic transmission may be interpreted as evidence of monosynaptic connection between pairs of cells \cite{Moore:1970,Alonso:1998,Denman:2013}. Without targeted stimulation of specific cells or measurement of intracellular signals, such analysis remains the best test for probable monosynaptic connections in vivo. At longer temporal scales, neural correlations reflect activations involving large ensembles of neurons. Such correlations may have emergent structure with little  correspondence to synaptic connectivity, which  may better reflect computations performed by the circuit.  For this reason, firing rate correlations at scales of tens or hundreds milliseconds have been of interest for their implications on coding under the assumption of rate codes and linear downstream decoder \cite{Averbeck:2006}. The terms \emph{functional connectivity} is still often applied to slow correlations, similarly to its use in PET, fMRI, EEG, and MEG brain imaging studies, as an expression of task-related, stimulus-evoked, or spontaneous synchronization or correlation between brain regions, circuits, or cells without implying a mechanistic interpretation.

@@

\subsection*{Correlation `structure'}
The term `structure' refers to a succinct, simplified representation that captures the essential features. Many questions in systems neuroscience require deducing the structure of the neural correlation structure in order to relate it to the spatial organization of the circuit, track its changes due to learning and development, or to describe effects of brain states, etc.  Perhaps the least sophisticated approach for extracting the structure of a correlation matrix is to examine the network of its most significant or largest coefficients.  For example, \cite{Malmersjo:2013} analyzed the graph theoretical properties of networks of thresholded correlations in development.  Alternatively, the correlation structure is often expressed through low-rank approximations extracted by principal component analysis or factor analysis. These components show synchronous multineuronal activation patterns without revealing graphs of interactions between neurons.  Another reduced representation of correlation matrices is obtained by sparsifying its inverse, resulting in a graph of partial correlations. Under the assumption of a multivariate normal distribution or, more generally, an elliptical distribution, sparse partial correlations suggest a sparse network of dependencies, \emph{i.e.}\;a probabilistic graphical model. This property has led some investigators to propose that such approximations  must  serve as closer estimates of direct interactions between brain regions in imaging studies than correlations \cite{Varoquaux:2012,Ryali:2012}. However, since deviations from elliptical distribution disrupt the correspondence between partial correlations and linear dependencies \cite{Loh:2012}, it is not clear whether that would indeed be the case. Partial correlations are meaningful when most interacting variables are observed. Perhaps for this reason, until now, parptial correlations had not been considered in analysis of multineuronal recordings.

We found that, for slow correlations (150 ms bins) in cortical microcircuits, networks of partial correlations were more statistically efficient than low-rank approximations of correlation matrices for cortical micr(Fig.\;S1 E), suggesting that they better reflected the correlation structure.  Furthermore, estimation was made even more efficient when low-rank components were allowed to be combined with partial correlations. The correlation structure depended more strongly on distance between cells and differences in their

\subsection*{Inference of functional connectivity with probabilistic models}
While synaptic connectivity constitutes a directed weighted graph, most meaningful representation of functional organization at longer temporal scales are less certain. A common approach has been to examine the low-rank structure of the joint population activity extracted through principal component analysis, factor analysis, independent component analysis, linear embedding, and others. Functional connectivity is then represented as the eigenvectors, principle components, or factor loadings corresponding to the extracted components of the joint activity.
